---
title: "Machine Learning"
author: "Milena Roesch"
date: "21 3 2021"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #2DC6D6;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE, cache.lazy = FALSE)
```
2020 | 9 | 3 Last compiled: `r Sys.Date()`

# Stock Data - Session 6 - Machine Learning Fundamentals
```{r}
# Libraries

library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(plotly)
library(ggrepel)
library(ggthemes)

# Load information ----
# STOCK PRICES
sp_500_prices_tbl <- read_rds("00_data/06_challenge/sp_500_prices_tbl.rds") %>%
  select("symbol", "date", "adjusted")
# SECTOR INFORMATION
sp_500_index_tbl <- read_rds("00_data/06_challenge/sp_500_index_tbl.rds") %>%
  select("company", "symbol", "sector")
# DAILY RETURNS
sp_500_daily_returns_tbl <- sp_500_prices_tbl %>%
  mutate(date = as.Date(date, "%Y-%M-%D")) %>%
  filter(date >= as.Date("2017-12-31")) %>%
  group_by(symbol) %>%
  mutate(previous_adjusted = lag(adjusted, n=1)) %>%
  filter(!is.na(previous_adjusted)) %>%
  mutate(pct_return = (adjusted - previous_adjusted)/previous_adjusted) %>%
  ungroup() %>%
  select("symbol", "date", "pct_return")

stock_date_matrix_tbl <- sp_500_daily_returns_tbl %>%
  pivot_wider(
    names_from = "date",
    values_from = "pct_return",
    values_fill = 0
  )

 
kmeans_mapper <- function(center) {
  stock_date_matrix_tbl %>%
    select(-symbol) %>%
    kmeans(centers = center, nstart = 20)
}


k_means_mapped_tbl <- tibble(centers = 1:30) %>%
  mutate(k_means = map(centers, kmeans_mapper)) %>%
  mutate(glance = map(k_means, glance))


# Visualize Scree Plot ----
k_means_mapped_tbl %>%
  unnest(glance) %>%
  select(centers, tot.withinss) %>%
  ggplot(aes(centers, tot.withinss)) +
  geom_point(color = "#2DC6D6", size = 4) +
  geom_line(color = "#2DC6D6", size = 1) +
  ggrepel::geom_label_repel(aes(label = centers), color = "#2DC6D6") +
  labs(
    title = "Scree Plot"
  )
# Visualization: UMAP ------
umap_results <- stock_date_matrix_tbl %>%
  select(-symbol) %>%
  umap()

# Convert umap results to tibble with symbols
umap_results_tbl <- umap_results$layout %>%
  as_tibble() %>%
  bind_cols(
    stock_date_matrix_tbl %>% select(symbol)
  )

# Visualize UMAP results
k_means_mapped_official_tbl <- read_rds("00_data/06_challenge/k_means_mapped_tbl.rds")
umap_results_official_tbl   <- read_rds("00_data/06_challenge/umap_results_tbl.rds")

umap_results_official_tbl %>%
  ggplot(aes(V1, V2)) + 
  geom_point(alpha=0.5) + 
  theme_tq() +
  labs(
    title = "UMAP Projection"
  )

# Combine K-means and UMAP ----
k_means_obj <- k_means_mapped_official_tbl %>%
  filter(centers == 10) %>%
  pull(k_means) %>%
  pluck(1)

umap_kmeans_results_tbl <- k_means_obj %>% 
  augment(stock_date_matrix_tbl) %>%
  select(symbol, .cluster) %>%
  left_join(umap_results_official_tbl, by = "symbol") %>%
  left_join((sp_500_index_tbl %>% select(symbol, company, sector)), by = "symbol")

# visualize combined k-means and umap results ----
ggplot(umap_kmeans_results_tbl, aes(V1, V2, color = .cluster)) +
  geom_point(
    na.rm = TRUE,
    alpha = 1/2
    ) +
  labs(
    title = "Visualization of k_means and UMAP results combined"
  ) +
  theme(legend.position = "none", 
  )
```

# Using a Recipe for the previous Business Case Analysis on Product Gaps and Pricing of our Bike Data - Session 7 & 8 - Supervised ML - Regression
```{r}
# Standard
library(tidyverse)
library(dplyr)

# Modeling
library(parsnip)

# Preprocessing & Sampling
library(recipes)
library(rsample)

# Workflows
library(workflows)

# Modeling Error Metrics
library(yardstick)

# Plotting Decision Trees
library(rpart.plot)

# Modeling ----------------------------------------------------------------
bike_orderlines_tbl <- readRDS("00_data/01_bike_sales/02_wrangled_data/bike_orderlines.rds")

model_sales_tbl <- bike_orderlines_tbl %>%
  select(total_price, model, category_2, frame_material) %>%

  group_by(model, category_2, frame_material) %>%
  summarise(total_sales = sum(total_price)) %>%
  ungroup() %>%

  arrange(desc(total_sales))

model_sales_tbl %>%
  mutate(category_2 = as_factor(category_2) %>%
           fct_reorder(total_sales, .fun = max) %>%
           fct_rev()) %>%
  ggplot(aes(frame_material, total_sales)) +
  geom_violin() +
  geom_jitter(width = 0.1, alpha = 0.5, color = "#2c3e50") +
  #coord_flip() +
  facet_wrap(~ category_2) +
  scale_y_continuous(labels = scales::dollar_format(scale = 1e-6, suffix = "M", accuracy = 0.1)) +
  tidyquant::theme_tq() +
  labs(
    title = "Total Sales for Each Model",
    x = "Frame Material", y = "Revenue"
  )

bike_features_tbl <- readRDS("00_data/01_bike_sales/02_wrangled_data/bike_features_tbl.rds")
names(bike_features_tbl) <- str_replace_all(names(bike_features_tbl), c(" " = "_" , "," = "" ))


# Set Shift Lever as alternative input if Rear Derailleur is na
bike_features_tbl$Rear_Derailleur[is.na(bike_features_tbl$Rear_Derailleur)] <- bike_features_tbl$Shift_Lever[is.na(bike_features_tbl$Rear_Derailleur)]
bike_features_tbl <- bike_features_tbl %>% 
  rename(Rear_Derailleur_Shift_Lever = Rear_Derailleur) %>%
  drop_na(Rear_Derailleur_Shift_Lever) %>%
  mutate(id = row_number()) 


# Splitting Data ----
set.seed(seed = 1113)
split_obj <- rsample::initial_split(bike_features_tbl, prop   = 0.80, 
                                    strata = "category_2")

# Check if testing contains all category_2 values
split_obj %>% training() %>% distinct(category_2)
split_obj %>% testing() %>% distinct(category_2)

# Assign training and test data
train_tbl <- training(split_obj)
test_tbl  <- testing(split_obj)

# Recipe
bike_features_rec <- 
  recipe( ~ ., data = train_tbl) %>%
  step_rm(all_predictors(), - Rear_Derailleur_Shift_Lever) %>% 
  step_dummy(all_nominal(), - all_outcomes()) %>%
  prep()

bike_transformed_tbl <- bake(bike_features_rec, new_data = NULL)

# Continue by putting in a workflow, test, etc. --> NOT PROCESSED THROUGH HERE
```

# Employee Attrition - Session 9 - Automated Machine Learning with H20 (I)
```{r}
# Standard
library(tidyverse)
library(readxl)
library(skimr)
library(GGally)


#Load data
employee_attrition_tbl <- read_csv("./00_data/09_automated_ML_h2o/datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")

dept_job_role_tbl <- employee_attrition_tbl %>%
  select(EmployeeNumber, Department, JobRole, PerformanceRating, Attrition)

# Business & Data Understanding: Department and Job Role ----
# Data subset
dept_job_role_tbl %>%
  group_by(Department, JobRole, Attrition)

# Function to convert counts to percentages.
count_to_pct <- function(data, ..., col = n) {

  # capture the dots
  grouping_vars_expr <- quos(...)
  col_expr <- enquo(col)

  ret <- data %>%
    group_by(!!! grouping_vars_expr) %>%
    mutate(pct = (!! col_expr) / sum(!! col_expr)) %>%
    ungroup()

  return(ret)

}

dept_job_role_tbl %>%
  count(JobRole, Attrition) %>%
  count_to_pct(JobRole)

dept_job_role_tbl %>%
  count(Department, JobRole, Attrition) %>%
  count_to_pct(Department, JobRole)

assess_attrition <- function(data, attrition_col, attrition_value, baseline_pct) {

  attrition_col_expr <- enquo(attrition_col)

  data %>%

    # Use parenthesis () to give tidy eval evaluation priority
    filter((!! attrition_col_expr) %in% attrition_value) %>%
    arrange(desc(pct)) %>%
    mutate(
      # Function inputs in numeric format (e.g. baseline_pct = 0.088 don't require tidy eval)
      above_industry_avg = case_when(
        pct > baseline_pct ~ "Yes",
        TRUE ~ "No"
      )
    )
}


# Attrition by job role
source("./00_scripts/9_assess_attrition.R")

# Function to calculate attrition cost ----
calculate_attrition_cost <- function(
  
  # Employee
  n                    = 1,
  salary               = 80000,
  
  # Direct Costs
  separation_cost      = 500,
  vacancy_cost         = 10000,
  acquisition_cost     = 4900,
  placement_cost       = 3500,
  
  # Productivity Costs
  net_revenue_per_employee = 250000,
  workdays_per_year        = 240,
  workdays_position_open   = 40,
  workdays_onboarding      = 60,
  onboarding_efficiency    = 0.50
  
) { 
  # Direct Costs
  direct_cost <- sum(separation_cost, vacancy_cost, acquisition_cost, placement_cost)
  
  # Lost Productivity Costs
  productivity_cost <- net_revenue_per_employee / workdays_per_year *
    (workdays_position_open + workdays_onboarding * onboarding_efficiency)
  
  # Savings of Salary & Benefits (Cost Reduction)
  salary_benefit_reduction <- salary / workdays_per_year * workdays_position_open
  
  # Estimated Turnover Per Employee
  cost_per_employee <- direct_cost + productivity_cost - salary_benefit_reduction
  
  # Total Cost of Employee Turnover
  total_cost <- n * cost_per_employee
  
  return(total_cost)
  
}

dept_job_role_tbl %>%
  
  count(Department, JobRole, Attrition) %>%
  count_to_pct(Department, JobRole) %>%
  assess_attrition(Attrition, attrition_value = "Yes", baseline_pct = 0.088) %>%
  mutate(
    cost_of_attrition = calculate_attrition_cost(n = n, salary = 80000)
  )

#Visualization ----
# Function to plot attrition
plot_attrition <- function(data, 
                           ..., 
                           .value,
                           fct_reorder = TRUE,
                           fct_rev     = FALSE,
                           include_lbl = TRUE,
                           color       = "#2dc6d6",
                           units       = c("0", "K", "M")) {
  
  ### Inputs
  group_vars_expr   <- quos(...)
  
  # If the user does not supply anything, 
  # this takes the first column of the supplied data
  if (length(group_vars_expr) == 0) {
    group_vars_expr <- quos(rlang::sym(colnames(data)[[1]]))
  }
  
  value_expr <- enquo(.value)
  
  units_val  <- switch(units[[1]],
                       "M" = 1e6,
                       "K" = 1e3,
                       "0" = 1)
  if (units[[1]] == "0") units <- ""
  
  # Data Manipulation
  # This is a so called Function Factory (a function that produces a function)
  usd <- scales::dollar_format(prefix = "$", largest_with_cents = 1e3)
  
  # Create the axis labels and values for the plot
  data_manipulated <- data %>%
    mutate(name = str_c(!!! group_vars_expr, sep = ": ") %>% as_factor()) %>%
    mutate(value_text = str_c(usd(!! value_expr / units_val),
                              units[[1]], sep = ""))
  
  
  # Order the labels on the y-axis according to the input
  if (fct_reorder) {
    data_manipulated <- data_manipulated %>%
      mutate(name = forcats::fct_reorder(name, !! value_expr)) %>%
      arrange(name)
  }
  
  if (fct_rev) {
    data_manipulated <- data_manipulated %>%
      mutate(name = forcats::fct_rev(name)) %>%
      arrange(name)
  }
  
  # Visualization
  g <- data_manipulated %>%
    
    # "name" is a column name generated by our function internally as part of the data manipulation task
    ggplot(aes(x = (!! value_expr), y = name)) +
    geom_segment(aes(xend = 0, yend = name), color = color) +
    geom_point(aes(size = !! value_expr), color = color) +
    scale_x_continuous(labels = scales::dollar) +
    scale_size(range = c(3, 5)) +
    theme(legend.position = "none")
  
  # Plot labels if TRUE
  if (include_lbl) {
    g <- g +
      geom_label(aes(label = value_text, size = !! value_expr),
                 hjust = "inward", color = color)
  }
  
  return(g)
  
}


#Visualization
dept_job_role_tbl %>%
  
  # Select columnns
  count(Department, JobRole, Attrition) %>%
  count_to_pct(Department, JobRole) %>%
  
  assess_attrition(Attrition, attrition_value = "Yes", baseline_pct = 0.088) %>%
  mutate(
    cost_of_attrition = calculate_attrition_cost(n = n, salary = 80000)
  ) %>%
  
  # Select columnns
  plot_attrition(Department, JobRole, .value = cost_of_attrition,
                 units = "M") +
  labs(
    title = "Estimated Cost of Attrition by Job Role",
    x = "Cost of Attrition",
    subtitle = "Looks like Sales Executive and Labaratory Technician are the biggest drivers of cost"
  )

# Data understanding -----
path_data_definitions <- "./00_data/09_automated_ML_h2o/data_definitions.xlsx"
definitions_raw_tbl   <- read_excel(path_data_definitions, sheet = 1, col_names = FALSE)

# Descriptive Features
employee_attrition_tbl %>% select(Age, DistanceFromHome, Gender, MaritalStatus, NumCompaniesWorked, Over18)

# Employment Features
employee_attrition_tbl %>% select(Department, EmployeeCount, EmployeeNumber, JobInvolvement, JobLevel, JobRole, JobSatisfaction)

# Compensation Features
employee_attrition_tbl %>% select(DailyRate, HourlyRate, MonthlyIncome, MonthlyRate, PercentSalaryHike, StockOptionLevel)

# Survery Results
employee_attrition_tbl %>% select(EnvironmentSatisfaction, JobSatisfaction, RelationshipSatisfaction, WorkLifeBalance)

# Performance Data
employee_attrition_tbl %>% select(JobInvolvement, PerformanceRating)

# Work-Life Features
employee_attrition_tbl %>% select(BusinessTravel, OverTime)

# Training & Education
employee_attrition_tbl %>% select(Education, EducationField, TrainingTimesLastYear)

# Time-Based Features
employee_attrition_tbl %>% select(TotalWorkingYears, YearsAtCompany, YearsInCurrentRole, YearsSinceLastPromotion, YearsWithCurrManager)


# Step 1: Data Summarization -----

skim(employee_attrition_tbl)

# Character Data Type
employee_attrition_tbl %>%
  select_if(is.character) %>%
  glimpse()

# Get "levels"
employee_attrition_tbl %>%
  select_if(is.character) %>%
  map(unique)

# Proportions    
employee_attrition_tbl %>%
  select_if(is.character) %>%
  map(~ table(.) %>% prop.table())

# Numeric Data
employee_attrition_tbl %>%
  select_if(is.numeric) %>%
  map(~ unique(.) %>% length())

employee_attrition_tbl %>%
  select_if(is.numeric) %>%
  map_df(~ unique(.) %>% length()) %>%
  # Select all columns
  pivot_longer(everything()) %>%
  arrange(value) %>%
  filter(value <= 10)

# Step 2: Data Visualization ----
employee_attrition_tbl %>%
  select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
  ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
          diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
  theme(legend.position = "bottom")

# Create data tibble, to potentially debug the plot_ggpairs function (because it has a data argument)
data <- employee_attrition_tbl %>%
  select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome)

plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
  
  color_expr <- enquo(color)
  
  if (rlang::quo_is_null(color_expr)) {
    
    g <- data %>%
      ggpairs(lower = "blank") 
    
  } else {
    
    color_name <- quo_name(color_expr)
    
    g <- data %>%
      ggpairs(mapping = aes_string(color = color_name), 
              lower = "blank", legend = 1,
              diag = list(continuous = wrap("densityDiag", 
                                            alpha = density_alpha))) +
      theme(legend.position = "bottom")
  }
  
  return(g)
  
}

employee_attrition_tbl %>%
  select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
  plot_ggpairs(color = Attrition)


# Explore Features by Category

#   1. Descriptive features: age, gender, marital status
employee_attrition_tbl %>%
  select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
  plot_ggpairs(Attrition)

#   2. Employment features: department, job role, job level
employee_attrition_tbl %>%
  select(Attrition, contains("employee"), contains("department"), contains("job")) %>%
  plot_ggpairs(Attrition)

#   3. Compensation features: HourlyRate, MonthlyIncome, StockOptionLevel
employee_attrition_tbl %>%
  select(Attrition, contains("income"), contains("rate"), contains("salary"), contains("stock")) %>%
  plot_ggpairs(Attrition)

#   4. Survey Results: Satisfaction level, WorkLifeBalance
employee_attrition_tbl %>%
  select(Attrition, contains("satisfaction"), contains("life")) %>%
  plot_ggpairs(Attrition)

#   5. Performance Data: Job Involvment, Performance Rating
employee_attrition_tbl %>%
  select(Attrition, contains("performance"), contains("involvement")) %>%
  plot_ggpairs(Attrition)

#   6. Work-Life Features
employee_attrition_tbl %>%
  select(Attrition, contains("overtime"), contains("travel")) %>%
  plot_ggpairs(Attrition)

#   7. Training and Education
employee_attrition_tbl %>%
  select(Attrition, contains("training"), contains("education")) %>%
  plot_ggpairs(Attrition)

#   8. Time-Based Features: Years at company, years in current role
employee_attrition_tbl %>%
  select(Attrition, contains("years")) %>%
  plot_ggpairs(Attrition)

# 1. Compensation Features What can you deduce about the interaction between Monthly Income and Attrition?
#   c. Those that are leaving have a lower Monthly Income
# 2. Compensation Features What can you deduce about the interaction between Percent Salary Hike and Attrition?
#   d. It’s difficult to deduce anything based on the visualization
# 3. Compensation Features What can you deduce about the interaction between Stock Option Level and Attrition?
#   b. Those that are staying have a higher stock option level
# 4. Survey Results What can you deduce about the interaction between Environment Satisfaction and Attrition?
#   a. A higher proportion of those leaving have a low environment satisfaction level
# 5. Survey Results What can you deduce about the interaction between Work Life Balance and Attrition?
#   b. Those that are staying have a higher density of 2’s and 3’s
# 6. Performance Data What Can you deduce about the interaction between Job Involvement and Attrition?
#   a. Those that are leaving have a lower density of 3’s and 4’s
# 7. Work-Life Features What can you deduce about the interaction between Over Time and Attrition?
#   a. The proportion of those leaving that are working Over Time are high compared to those that are not leaving
# 8. Training and Education What can you deduce about the interaction between Training Times Last Year and Attrition
#   b. People that leave tend to have less annual trainings
# 9. Time-Based Features What can you deduce about the interaction between Years At Company and Attrition
#   b. People that leave tend to have less working years at the company
# 10. Time-Based Features What can you deduce about the interaction between Years Since Last Promotion and Attrition?
#   c. It’s difficult to deduce anything based on the visualization

```

# Business Case on Employee Attrition and Product Backorders Challenge - Session 10 - Automated Machine Learning with H20 (II)
## Business Case
```{r}
# Load data
library(tidyverse)
library(readxl)
library(rsample)
library(recipes)
library(PerformanceAnalytics)  
library(h2o)

process_hr_data_readable <- function(data, definitions_tbl) {
  
  definitions_list <- definitions_tbl %>%
    fill(...1, .direction = "down") %>%
    filter(!is.na(...2)) %>%
    separate(...2, into = c("key", "value"), sep = " '", remove = TRUE) %>%
    rename(column_name = ...1) %>%
    mutate(key = as.numeric(key)) %>%
    mutate(value = value %>% str_replace(pattern = "'", replacement = "")) %>%
    split(.$column_name) %>%
    map(~ select(., -column_name)) %>%
    map(~ mutate(., value = as_factor(value))) 
  
  for (i in seq_along(definitions_list)) {
    list_name <- names(definitions_list)[i]
    colnames(definitions_list[[i]]) <- c(list_name, paste0(list_name, "_value"))
  }
  
  data_merged_tbl <- list(HR_Data = data) %>%
    append(definitions_list, after = 1) %>%
    reduce(left_join) %>%
    select(-one_of(names(definitions_list))) %>%
    set_names(str_replace_all(names(.), pattern = "_value", 
                              replacement = "")) %>%
    select(sort(names(.))) %>%
    mutate_if(is.character, as.factor) %>%
    mutate(
      BusinessTravel = BusinessTravel %>% fct_relevel("Non-Travel", 
                                                      "Travel_Rarely", 
                                                      "Travel_Frequently"),
      MaritalStatus  = MaritalStatus %>% fct_relevel("Single", 
                                                     "Married", 
                                                     "Divorced")
    )
  
  return(data_merged_tbl)
  
}


# H2O Modelling

employee_attrition_tbl          <- read_csv("./00_data/09_automated_ML_h2o/datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")
definitions_raw_tbl             <- read_excel("./00_data/09_automated_ML_h2o/data_definitions.xlsx", sheet = 1, col_names = FALSE)
employee_attrition_readable_tbl <- process_hr_data_readable(employee_attrition_tbl, definitions_raw_tbl)
set.seed(seed = 1113)
split_obj                       <- rsample::initial_split(employee_attrition_readable_tbl, prop = 0.85)
train_readable_tbl              <- training(split_obj)
test_readable_tbl               <- testing(split_obj)

recipe_obj <- recipe(Attrition ~., data = train_readable_tbl) %>% 
  step_zv(all_predictors()) %>% 
  step_mutate_at(JobLevel, StockOptionLevel, fn = as.factor) %>% 
  prep()

train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)

# Modeling
h2o.init()

# Split data into a training and a validation data frame
# Setting the seed is just for reproducability
split_h2o <- h2o.splitFrame(as.h2o(train_tbl), ratios = c(0.85), seed = 1234)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o  <- as.h2o(test_tbl)

# Set the target and predictors
y <- "Attrition"
x <- setdiff(names(train_h2o), y)


automl_models_h2o <- h2o.automl(
  x = x,
  y = y,
  training_frame    = train_h2o,
  validation_frame  = valid_h2o,
  leaderboard_frame = test_h2o,
  max_runtime_secs  = 30,
  nfolds            = 5 
)

typeof(automl_models_h2o)
slotNames(automl_models_h2o)
automl_models_h2o@leaderboard
automl_models_h2o@leader

# Extracts and H2O model name by a position so can more easily use h2o.getModel()
extract_h2o_model_name_by_position <- function(h2o_leaderboard, n = 1, verbose = T) {
  
  model_name <- h2o_leaderboard %>%
    as.tibble() %>%
    slice(n) %>%
    pull(model_id)
  
  if (verbose) message(model_name)
  
  return(model_name)
  
}

automl_models_h2o@leaderboard %>% 
  extract_h2o_model_name_by_position(6) %>% 
  h2o.getModel()

```

## Challenge
```{r}
library(h2o)
library(tidyverse)
library(readxl)
library(rsample)
library(recipes)
library(PerformanceAnalytics)

# Load data
product_backorders_tbl          <- read_csv("./00_data/10_automated_ML_h2o_II/product_backorders.csv")

# Split data into test and train data
set.seed(seed = 1113)
split_obj                       <- rsample::initial_split(product_backorders_tbl, prop = 0.85)
train_readable_tbl              <- training(split_obj)
test_readable_tbl               <- testing(split_obj)

# Recipe
recipe_obj <- recipe(went_on_backorder ~., data = train_readable_tbl) %>% 
  step_zv(all_predictors()) %>% 
  prep()

# Bake Recipe
train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)

# Modeling
h2o.init()

# Split data into a training and a validation data frame
# Setting the seed is just for reproducability
split_h2o <- h2o.splitFrame(as.h2o(train_tbl), ratios = c(0.85), seed = 1234)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o  <- as.h2o(test_tbl)

# Set the target and predictors
y <- "went_on_backorder"
x <- setdiff(names(train_h2o), y)

automl_models_h2o <- h2o.automl(
  x = x,
  y = y,
  training_frame    = train_h2o,
  validation_frame  = valid_h2o,
  leaderboard_frame = test_h2o,
  max_runtime_secs  = 30,
  nfolds            = 5 
)

typeof(automl_models_h2o)

slotNames(automl_models_h2o)

automl_models_h2o@leaderboard

# Depending on the algorithm, the output will be different
#h2o.getModel("StackedEnsemble_AllModels_AutoML_20210129_132920")

# Extracts and H2O model name by a position so can more easily use h2o.getModel()
extract_h2o_model_name_by_position <- function(h2o_leaderboard, n = 1, verbose = T) {
  
  model_name <- h2o_leaderboard %>%
    as_tibble() %>%
    slice(n) %>%
    pull(model_id)
  
  if (verbose) message(model_name)
  
  return(model_name)
  
}

automl_models_h2o@leaderboard %>% 
  extract_h2o_model_name_by_position(6) %>% 
  h2o.getModel()

#Save model
# h2o.getModel("StackedEnsemble_AllModels_AutoML_20210129_132920") %>%
#   h2o.saveModel(path = "04_model/h2o_models/")

h2o.loadModel("04_Model/h2o_models/StackedEnsemble_AllModels_AutoML_20210129_132920")
stacked_ensemble_h2o <- h2o.loadModel("04_model/h2o_models/StackedEnsemble_AllModels_AutoML_20210129_132920")
stacked_ensemble_h2o

predictions <- h2o.predict(stacked_ensemble_h2o, newdata = as.h2o(test_tbl))

typeof(predictions)

predictions_tbl <- predictions %>% as_tibble()

deep_learning_h2o <- h2o.loadModel("04_model/h2o_models/StackedEnsemble_AllModels_AutoML_20210129_132920")
deep_learning_h2o@allparameters
```

# Applying a Performance Analysis on the previous Product Backorders Challenge - Session 11 - Performance Measures
```{r}
library(h2o)
library(tidyverse)
library(readxl)
library(rsample)
library(recipes)
library(PerformanceAnalytics)
library(cowplot)
library(glue)
library(purrr)

#From last session -----
# Load data
product_backorders_tbl          <- read_csv("./00_data/10_automated_ML_h2o_II/product_backorders.csv")

# Split data into test and train data
set.seed(seed = 1113)
split_obj                       <- rsample::initial_split(product_backorders_tbl, prop = 0.85)
train_readable_tbl              <- training(split_obj)
test_readable_tbl               <- testing(split_obj)

# Recipe
recipe_obj <- recipe(went_on_backorder ~., data = train_readable_tbl) %>% 
  step_zv(all_predictors()) %>% 
  prep()

# Bake Recipe
train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)

# Modeling
h2o.init()

# Split data into a training and a validation data frame
# Setting the seed is just for reproducability
split_h2o <- h2o.splitFrame(as.h2o(train_tbl), ratios = c(0.85), seed = 1234)
train_h2o <- split_h2o[[1]]
valid_h2o <- split_h2o[[2]]
test_h2o  <- as.h2o(test_tbl)

# Set the target and predictors
y <- "went_on_backorder"
x <- setdiff(names(train_h2o), y)

automl_models_h2o <- h2o.automl(
  x = x,
  y = y,
  training_frame    = train_h2o,
  validation_frame  = valid_h2o,
  leaderboard_frame = test_h2o,
  max_runtime_secs  = 30,
  nfolds            = 5 
)

typeof(automl_models_h2o)

slotNames(automl_models_h2o)

automl_models_h2o@leaderboard

# Depending on the algorithm, the output will be different
automl_models_h2o@leaderboard %>% 
  as_tibble() %>% 
  select(-c(mean_per_class_error, rmse, mse))

# Save models
# h2o.getModel("StackedEnsemble_AllModels_AutoML_20210129_162602") %>% 
#   h2o.saveModel(path = "04_model/h2o_models/")
# h2o.getModel("DeepLearning_1_AutoML_20210129_162602") %>% 
#   h2o.saveModel(path = "04_model/h2o_models/")

# Visualization of the H2O Leaderboard to help model selection ----
data_transformed_tbl <- automl_models_h2o@leaderboard %>%
  as_tibble() %>%
  select(-c(aucpr, mean_per_class_error, rmse, mse)) %>% 
  mutate(model_type = str_extract(model_id, "[^_]+")) %>%
  slice(1:15) %>% 
  rownames_to_column(var = "rowname") %>%
  # Visually this step will not change anything
  # It reorders the factors under the hood
  mutate(
    model_id   = as_factor(model_id) %>% reorder(auc),
    model_type = as.factor(model_type)
  ) %>% 
  pivot_longer(cols = -c(model_id, model_type, rowname), 
               names_to = "key", 
               values_to = "value", 
               names_transform = list(key = forcats::fct_inorder)
  ) %>% 
  mutate(model_id = paste0(rowname, ". ", model_id) %>% as_factor() %>% fct_rev())

data_transformed_tbl %>%
  ggplot(aes(value, model_id, color = model_type)) +
  geom_point(size = 3) +
  geom_label(aes(label = round(value, 2), hjust = "inward")) +
  
  # Facet to break out logloss and auc
  facet_wrap(~ key, scales = "free_x") +
  labs(title = "Leaderboard Metrics",
       subtitle = paste0("Ordered by: ", "auc"),
       y = "Model Postion, Model ID", x = "") + 
  theme(legend.position = "bottom")

plot_h2o_leaderboard <- function(h2o_leaderboard, order_by = c("auc", "logloss"), 
                                 n_max = 20, size = 4, include_lbl = TRUE) {
  
  # Setup inputs
  # adjust input so that all formats are working
  order_by <- tolower(order_by[[1]])
  
  leaderboard_tbl <- h2o_leaderboard %>%
    as.tibble() %>%
    select(-c(aucpr, mean_per_class_error, rmse, mse)) %>% 
    mutate(model_type = str_extract(model_id, "[^_]+")) %>%
    rownames_to_column(var = "rowname") %>%
    mutate(model_id = paste0(rowname, ". ", model_id) %>% as.factor())
  
  # Transformation
  if (order_by == "auc") {
    
    data_transformed_tbl <- leaderboard_tbl %>%
      slice(1:n_max) %>%
      mutate(
        model_id   = as_factor(model_id) %>% reorder(auc),
        model_type = as.factor(model_type)
      ) %>%
      pivot_longer(cols = -c(model_id, model_type, rowname), 
                   names_to = "key", 
                   values_to = "value", 
                   names_transform = list(key = forcats::fct_inorder)
      )
    
  } else if (order_by == "logloss") {
    
    data_transformed_tbl <- leaderboard_tbl %>%
      slice(1:n_max) %>%
      mutate(
        model_id   = as_factor(model_id) %>% reorder(logloss) %>% fct_rev(),
        model_type = as.factor(model_type)
      ) %>%
      pivot_longer(cols = -c(model_id, model_type, rowname), 
                   names_to = "key", 
                   values_to = "value", 
                   names_transform = list(key = forcats::fct_inorder)
      )
    
  } else {
    # If nothing is supplied
    stop(paste0("order_by = '", order_by, "' is not a permitted option."))
  }
  
  # Visualization of transformed data
  g <- data_transformed_tbl %>%
    ggplot(aes(value, model_id, color = model_type)) +
    geom_point(size = size) +
    facet_wrap(~ key, scales = "free_x") +
    labs(title = "Leaderboard Metrics",
         subtitle = paste0("Ordered by: ", toupper(order_by)),
         y = "Model Postion, Model ID", x = "")
  
  if (include_lbl) g <- g + geom_label(aes(label = round(value, 2), 
                                           hjust = "inward"))
  
  return(g)
  
}

# Tune model with grid search ----
deeplearning_h2o <- h2o.loadModel("04_model/h2o_models/DeepLearning_1_AutoML_20210129_162602")
deeplearning_h2o

# We want to see how it performs for the testing data frame
test_tbl

h2o.performance(deeplearning_h2o, newdata = as.h2o(test_tbl))


# Visualize trade off btw precision, recall and optimal threshold
deeplearning_grid_01 <- h2o.grid(
  algorithm = "deeplearning",
  grid_id = "deeplearning_grid_01",
  x = x,
  y = y,
  training_frame   = train_h2o,
  validation_frame = valid_h2o,
  nfolds = 5,
  
  # Hyperparamters: Use deeplearning_h2o@allparameters to see all
  hyper_params = list(
    # Use some combinations (the first one was the original)
    hidden = list(c(10, 10, 10), c(50, 20, 10), c(20, 20, 20)),
    epochs = c(10, 50, 100)
  )
)

deeplearning_grid_01

h2o.getGrid(grid_id = "deeplearning_grid_01", sort_by = "auc", decreasing = TRUE)

deeplearning_grid_01_model_1 <- h2o.getModel("DeepLearning_1_AutoML_20210129_162602")
deeplearning_grid_01_model_1 %>% h2o.auc(train = T, valid = T, xval = T)

# Run it on the test data
deeplearning_grid_01_model_1 %>%
  h2o.performance(newdata = as.h2o(test_tbl))

# Assessing Performance -----
stacked_ensemble_h2o <- h2o.loadModel("04_model/h2o_models/StackedEnsemble_AllModels_AutoML_20210129_162602")
# Create a performance object
performance_h2o <- h2o.performance(stacked_ensemble_h2o, newdata = as.h2o(test_tbl))

typeof(performance_h2o)

performance_h2o %>% slotNames()

# We are focusing on the slot metrics. This slot contains all possible metrics
performance_h2o@metrics
# Classifier Summary Metrics
h2o.auc(performance_h2o, train = T, valid = T, xval = T)
h2o.auc(stacked_ensemble_h2o, train = T, valid = T, xval = T)
h2o.giniCoef(performance_h2o)
h2o.logloss(performance_h2o)
h2o.confusionMatrix(stacked_ensemble_h2o)
h2o.confusionMatrix(performance_h2o)

performance_tbl <- performance_h2o %>%
  h2o.metric() %>%
  as.tibble() 

performance_tbl %>% 
  glimpse()

theme_new <- theme(
  legend.position  = "bottom",
  legend.key       = element_blank(),
  panel.background = element_rect(fill   = "transparent"),
  panel.border     = element_rect(color = "black", fill = NA, size = 0.5),
  panel.grid.major = element_line(color = "grey", size = 0.333)
) 

h2o.init()

performance_tbl %>%
  filter(f1 == max(f1))

performance_tbl %>%
  ggplot(aes(x = threshold)) +
  geom_line(aes(y = precision), color = "pink", size = 1) +
  geom_line(aes(y = recall), color = "purple", size = 1) +
  
  # Insert line where precision and recall are harmonically optimized
  geom_vline(xintercept = h2o.find_threshold_by_max_metric(performance_h2o, "f1")) +
  labs(title = "Precision vs Recall", y = "value") +
  theme_new

# ROC Plot ------
path <- "StackedEnsemble_AllModels_AutoML_20210129_162602"

load_model_performance_metrics <- function(path, test_tbl) {
  
  model_h2o <- h2o.loadModel(path)
  perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_tbl)) 
  
  perf_h2o %>%
    h2o.metric() %>%
    as_tibble() %>%
    mutate(auc = h2o.auc(perf_h2o)) %>%
    select(tpr, fpr, auc, precision, recall)
  
}

model_metrics_tbl <- fs::dir_info(path = "04_model/h2o_models/") %>%
  select(path) %>%
  mutate(metrics = purrr::map(path, load_model_performance_metrics, test_tbl)) %>%
  unnest(cols = metrics)

model_metrics_tbl %>%
  mutate(
    # Extract the model names
    path = str_split(path, pattern = "/", simplify = T)[,3] %>% as_factor(),
    auc  = auc %>% round(3) %>% as.character() %>% as_factor()
  ) %>%
  ggplot(aes(fpr, tpr, color = path, linetype = auc)) +
  geom_line(size = 1) +
  # just for demonstration purposes
  geom_abline(color = "purple", linetype = "dotted") +
  theme_new +
  theme(
    legend.direction = "vertical",
  ) +
  labs(
    title = "ROC Plot",
    subtitle = "Performance of 3 Top Performing Models"
  )

# Precision vs Recall Plot----
h2o.init()

model_metrics_tbl %>%
  mutate(
    path = str_split(path, pattern = "/", simplify = T)[,3] %>% as_factor(),
    auc  = auc %>% round(3) %>% as.character() %>% as_factor()
  ) %>%
  ggplot(aes(recall, precision, color = path, linetype = auc)) +
  geom_line(size = 1) +
  theme_new +
  theme(
    legend.direction = "vertical",
  ) +
  labs(
    title = "Precision vs Recall Plot",
    subtitle = "Performance of 3 Top Performing Models"
  )

# Gain and Lift
# data from last session 
stacked_ensemble_h2o <- h2o.loadModel("04_model/h2o_models/StackedEnsemble_AllModels_AutoML_20210129_132920")
predictions <- h2o.predict(stacked_ensemble_h2o, newdata = as.h2o(test_tbl))

typeof(predictions)

predictions_tbl <- predictions %>% as_tibble()

ranked_predictions_tbl <- predictions_tbl %>%
  bind_cols(test_tbl) %>%
  select(predict:Yes, went_on_backorder) %>%
  # Sorting from highest to lowest class probability
  arrange(desc(Yes))
calculated_gain_lift_tbl <- ranked_predictions_tbl %>%
  mutate(ntile = ntile(Yes, n = 10)) %>%
  group_by(ntile) %>%
  summarise(
    cases = n(),
    responses = sum(went_on_backorder == "Yes")
  ) %>%
  arrange(desc(ntile)) %>%
  
  # Add group numbers (opposite of ntile)
  mutate(group = row_number()) %>%
  select(group, cases, responses) %>%
  
  # Calculations
  mutate(
    cumulative_responses = cumsum(responses),
    pct_responses        = responses / sum(responses),
    gain                 = cumsum(pct_responses),
    cumulative_pct_cases = cumsum(cases) / sum(cases),
    lift                 = gain / cumulative_pct_cases,
    gain_baseline        = cumulative_pct_cases,
    lift_baseline        = gain_baseline / cumulative_pct_cases
  )
calculated_gain_lift_tbl 

gain_lift_tbl <- performance_h2o %>%
  h2o.gainsLift() %>%
  as.tibble()
gain_lift_tbl

# Gain
gain_transformed_tbl <- gain_lift_tbl %>% 
  select(group, cumulative_data_fraction, cumulative_capture_rate, cumulative_lift) %>%
  select(-contains("lift")) %>%
  mutate(baseline = cumulative_data_fraction) %>%
  rename(gain     = cumulative_capture_rate) %>%
  # prepare the data for the plotting (for the color and group aesthetics)
  pivot_longer(cols = c(gain, baseline), values_to = "value", names_to = "key")
gain_transformed_tbl %>%
  ggplot(aes(x = cumulative_data_fraction, y = value, color = key)) +
  geom_line(size = 1.5) +
  labs(
    title = "Gain Chart",
    x = "Cumulative Data Fraction",
    y = "Gain"
  ) +
  theme_new

# Lift 
lift_transformed_tbl <- gain_lift_tbl %>% 
  select(group, cumulative_data_fraction, cumulative_capture_rate, cumulative_lift) %>%
  select(-contains("capture")) %>%
  mutate(baseline = 1) %>%
  rename(lift = cumulative_lift) %>%
  pivot_longer(cols = c(lift, baseline), values_to = "value", names_to = "key")
lift_transformed_tbl %>%
  ggplot(aes(x = cumulative_data_fraction, y = value, color = key)) +
  geom_line(size = 1.5) +
  labs(
    title = "Lift Chart",
    x = "Cumulative Data Fraction",
    y = "Lift"
  ) +
  theme_new

# Dashboard cowplot
h2o_leaderboard <- automl_models_h2o@leaderboard
newdata <- test_tbl
order_by <- "auc"
max_models <- 4
size <- 1

plot_h2o_performance <- function(h2o_leaderboard, newdata, order_by = c("auc", "logloss"),
                                 max_models = 3, size = 1.5) {
  # Inputs
  leaderboard_tbl <- h2o_leaderboard %>%
    as_tibble() %>%
    slice(1:max_models)
  newdata_tbl <- newdata %>%
    as_tibble()
  # Selecting the first, if nothing is provided
  order_by      <- tolower(order_by[[1]]) 
  # Convert string stored in a variable to column name (symbol)
  order_by_expr <- rlang::sym(order_by)
  # Turn of the progress bars ( opposite h2o.show_progress())
  h2o.no_progress()
  # 1. Model metrics
  get_model_performance_metrics <- function(model_id, test_tbl) {
    model_h2o <- h2o.getModel(model_id)
    perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_tbl))
    perf_h2o %>%
      h2o.metric() %>%
      as.tibble() %>%
      select(threshold, tpr, fpr, precision, recall)
  }
  model_metrics_tbl <- leaderboard_tbl %>%
    mutate(metrics = map(model_id, get_model_performance_metrics, newdata_tbl)) %>%
    unnest(cols = metrics) %>%
    mutate(
      model_id = as_factor(model_id) %>% 
        # programmatically reorder factors depending on order_by
        fct_reorder(!! order_by_expr, 
                    .desc = ifelse(order_by == "auc", TRUE, FALSE)),
      auc      = auc %>% 
        round(3) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id)),
      logloss  = logloss %>% 
        round(4) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id))
    )
  
  # 1A. ROC Plot
  
  p1 <- model_metrics_tbl %>%
    ggplot(aes(fpr, tpr, color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size) +
    theme_new +
    labs(title = "ROC", x = "FPR", y = "TPR") +
    theme(legend.direction = "vertical") 
  
  
  # 1B. Precision vs Recall
  
  p2 <- model_metrics_tbl %>%
    ggplot(aes(recall, precision, color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size) +
    theme_new +
    labs(title = "Precision Vs Recall", x = "Recall", y = "Precision") +
    theme(legend.position = "none") 
  
  
  # 2. Gain / Lift
  
  get_gain_lift <- function(model_id, test_tbl) {
    
    model_h2o <- h2o.getModel(model_id)
    perf_h2o  <- h2o.performance(model_h2o, newdata = as.h2o(test_tbl)) 
    
    perf_h2o %>%
      h2o.gainsLift() %>%
      as.tibble() %>%
      select(group, cumulative_data_fraction, cumulative_capture_rate, cumulative_lift)
    
  }
  
  gain_lift_tbl <- leaderboard_tbl %>%
    mutate(metrics = map(model_id, get_gain_lift, newdata_tbl)) %>%
    unnest(cols = metrics) %>%
    mutate(
      model_id = as_factor(model_id) %>% 
        fct_reorder(!! order_by_expr, 
                    .desc = ifelse(order_by == "auc", TRUE, FALSE)),
      auc  = auc %>% 
        round(3) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id)),
      logloss = logloss %>% 
        round(4) %>% 
        as.character() %>% 
        as_factor() %>% 
        fct_reorder(as.numeric(model_id))
    ) %>%
    rename(
      gain = cumulative_capture_rate,
      lift = cumulative_lift
    ) 
  
  # 2A. Gain Plot
  
  p3 <- gain_lift_tbl %>%
    ggplot(aes(cumulative_data_fraction, gain, 
               color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size,) +
    geom_segment(x = 0, y = 0, xend = 1, yend = 1, 
                 color = "red", size = size, linetype = "dotted") +
    theme_new +
    expand_limits(x = c(0, 1), y = c(0, 1)) +
    labs(title = "Gain",
         x = "Cumulative Data Fraction", y = "Gain") +
    theme(legend.position = "none")
  
  # 2B. Lift Plot
  
  p4 <- gain_lift_tbl %>%
    ggplot(aes(cumulative_data_fraction, lift, 
               color = model_id, linetype = !! order_by_expr)) +
    geom_line(size = size) +
    geom_segment(x = 0, y = 1, xend = 1, yend = 1, 
                 color = "red", size = size, linetype = "dotted") +
    theme_new +
    expand_limits(x = c(0, 1), y = c(0, 1)) +
    labs(title = "Lift",
         x = "Cumulative Data Fraction", y = "Lift") +
    theme(legend.position = "none") 
  
  
  # Combine using cowplot
  
  # cowplot::get_legend extracts a legend from a ggplot object
  p_legend <- get_legend(p1)
  # Remove legend from p1
  p1 <- p1 + theme(legend.position = "none")
  
  # cowplot::plt_grid() combines multiple ggplots into a single cowplot object
  p <- cowplot::plot_grid(p1, p2, p3, p4, ncol = 2)
  
  # cowplot::ggdraw() sets up a drawing layer
  p_title <- ggdraw() + 
    
    # cowplot::draw_label() draws text on a ggdraw layer / ggplot object
    draw_label("H2O Model Metrics", size = 18, fontface = "bold", 
               color = "#2C3E50")
  
  p_subtitle <- ggdraw() + 
    draw_label(glue("Ordered by {toupper(order_by)}"), size = 10,  
               color = "#2C3E50")
  
  # Combine everything
  ret <- plot_grid(p_title, p_subtitle, p, p_legend, 
                   
                   # Adjust the relative spacing, so that the legends always fits
                   ncol = 1, rel_heights = c(0.05, 0.05, 1, 0.05 * max_models))
  
  h2o.show_progress()
  
  return(ret)
  
}



automl_models_h2o@leaderboard %>%
  plot_h2o_performance(newdata = test_tbl, order_by = "logloss", 
                       size = 0.5, max_models = 4)
```

# Session - 12 - LIME
## Part I
```{r}
library(h2o)
library(recipes)
library(readxl)
library(tidyverse)
library(tidyquant)
library(lime)
library(rsample)
library(recipes)

process_hr_data_readable <- function(data, definitions_tbl) {
  
  definitions_list <- definitions_tbl %>%
    fill(...1, .direction = "down") %>%
    filter(!is.na(...2)) %>%
    separate(...2, into = c("key", "value"), sep = " '", remove = TRUE) %>%
    rename(column_name = ...1) %>%
    mutate(key = as.numeric(key)) %>%
    mutate(value = value %>% str_replace(pattern = "'", replacement = "")) %>%
    split(.$column_name) %>%
    map(~ select(., -column_name)) %>%
    map(~ mutate(., value = as_factor(value))) 
  
  for (i in seq_along(definitions_list)) {
    list_name <- names(definitions_list)[i]
    colnames(definitions_list[[i]]) <- c(list_name, paste0(list_name, "_value"))
  }
  
  data_merged_tbl <- list(HR_Data = data) %>%
    append(definitions_list, after = 1) %>%
    reduce(left_join) %>%
    select(-one_of(names(definitions_list))) %>%
    set_names(str_replace_all(names(.), pattern = "_value", 
                              replacement = "")) %>%
    select(sort(names(.))) %>%
    mutate_if(is.character, as.factor) %>%
    mutate(
      BusinessTravel = BusinessTravel %>% fct_relevel("Non-Travel", 
                                                      "Travel_Rarely", 
                                                      "Travel_Frequently"),
      MaritalStatus  = MaritalStatus %>% fct_relevel("Single", 
                                                     "Married", 
                                                     "Divorced")
    )
  
  return(data_merged_tbl)
  
}

# Load Data
employee_attrition_tbl <- read_csv("./00_data/09_automated_ML_h2o/datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")
definitions_raw_tbl    <- read_excel("./00_data/09_automated_ML_h2o/data_definitions.xlsx", sheet = 1, col_names = FALSE)

employee_attrition_readable_tbl <- process_hr_data_readable(employee_attrition_tbl, definitions_raw_tbl)

# Split into test and train
set.seed(seed = 1113)
split_obj <- rsample::initial_split(employee_attrition_readable_tbl, prop = 0.85)

# Assign training and test data
train_readable_tbl <- training(split_obj)
test_readable_tbl  <- testing(split_obj)

# ML Preprocessing Recipe 
recipe_obj <- recipe(Attrition ~ ., data = train_readable_tbl) %>%
  step_zv(all_predictors()) %>%
  step_mutate_at(c("JobLevel", "StockOptionLevel"), fn = as.factor) %>% 
  prep()


train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)


# 2. Models ----

h2o.init()

automl_leader <- h2o.loadModel("./04_Model/Business_Case_Employee_Attrition/GLM_1_AutoML_20210130_000114")


# 3. LIME ----

# 3.1 Making Predictions ----

predictions_tbl <- automl_leader %>% 
  h2o.predict(newdata = as.h2o(test_tbl)) %>%
  as.tibble() %>%
  bind_cols(
    test_tbl %>%
      select(Attrition, EmployeeNumber)
  )

test_tbl %>%
  slice(1)

# 3.2 Single Explanation ----

explainer <- train_tbl %>%
  select(-Attrition) %>%
  lime(
    model           = automl_leader,
    bin_continuous  = TRUE,
    n_bins          = 4,
    quantile_bins   = TRUE
  )

explanation <- test_tbl %>%
  slice(1) %>%
  select(-Attrition) %>%
  lime::explain(
    
    # Pass our explainer object
    explainer = explainer,
    # Because it is a binary classification model: 1
    n_labels   = 1,
    # number of features to be returned
    n_features = 8,
    # number of localized linear models
    n_permutations = 5000,
    # Let's start with 1
    kernel_width   = 1
  )

explanation %>% 
  as.tibble()

case_1 <- explanation %>%
  filter(case == 1)

case_1 %>%
  ggplot(aes(feature_desc, feature_weight)) +
  coord_flip() +
  geom_col(fill = ifelse(case_1$feature_weight>0,"#2A6AA4","#851800"))
```

## Part II 
```{r}
library(h2o)
library(recipes)
library(readxl)
library(tidyverse)
library(tidyquant)
library(lime)
library(rsample)
library(dplyr)
library(stringr)

process_hr_data_readable <- function(data, definitions_tbl) {
  
  definitions_list <- definitions_tbl %>%
    fill(...1, .direction = "down") %>%
    filter(!is.na(...2)) %>%
    separate(...2, into = c("key", "value"), sep = " '", remove = TRUE) %>%
    rename(column_name = ...1) %>%
    mutate(key = as.numeric(key)) %>%
    mutate(value = value %>% str_replace(pattern = "'", replacement = "")) %>%
    split(.$column_name) %>%
    map(~ select(., -column_name)) %>%
    map(~ mutate(., value = as_factor(value))) 
  
  for (i in seq_along(definitions_list)) {
    list_name <- names(definitions_list)[i]
    colnames(definitions_list[[i]]) <- c(list_name, paste0(list_name, "_value"))
  }
  
  data_merged_tbl <- list(HR_Data = data) %>%
    append(definitions_list, after = 1) %>%
    reduce(left_join) %>%
    select(-one_of(names(definitions_list))) %>%
    set_names(str_replace_all(names(.), pattern = "_value", 
                              replacement = "")) %>%
    select(sort(names(.))) %>%
    mutate_if(is.character, as.factor) %>%
    mutate(
      BusinessTravel = BusinessTravel %>% fct_relevel("Non-Travel", 
                                                      "Travel_Rarely", 
                                                      "Travel_Frequently"),
      MaritalStatus  = MaritalStatus %>% fct_relevel("Single", 
                                                     "Married", 
                                                     "Divorced")
    )
  
  return(data_merged_tbl)
  
}

# Load Data
employee_attrition_tbl <- read_csv("./00_data/09_automated_ML_h2o/datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")
definitions_raw_tbl    <- read_excel("./00_data/09_automated_ML_h2o/data_definitions.xlsx", sheet = 1, col_names = FALSE)

employee_attrition_readable_tbl <- process_hr_data_readable(employee_attrition_tbl, definitions_raw_tbl)

# Split into test and train
set.seed(seed = 1113)
split_obj <- rsample::initial_split(employee_attrition_readable_tbl, prop = 0.85)

# Assign training and test data
train_readable_tbl <- training(split_obj)
test_readable_tbl  <- testing(split_obj)

# ML Preprocessing Recipe 
recipe_obj <- recipe(Attrition ~ ., data = train_readable_tbl) %>%
  step_zv(all_predictors()) %>%
  step_mutate_at(c("JobLevel", "StockOptionLevel"), fn = as.factor) %>% 
  prep()

train_tbl <- bake(recipe_obj, new_data = train_readable_tbl)
test_tbl  <- bake(recipe_obj, new_data = test_readable_tbl)


# 2. Models ----

h2o.init()

automl_leader <- h2o.loadModel("./04_Model/Business_Case_Employee_Attrition/GLM_1_AutoML_20210130_000114")

# 3. LIME ----

# 3.1 Making Predictions ----

predictions_tbl <- automl_leader %>% 
  h2o.predict(newdata = as.h2o(test_tbl)) %>%
  as.tibble() %>%
  bind_cols(
    test_tbl %>%
      select(Attrition, EmployeeNumber)
  )

test_tbl %>%
  slice(1)

# Multiple Explanations ----

explainer <- train_tbl %>%
  select(-Attrition) %>%
  lime(
    model           = automl_leader,
    bin_continuous  = TRUE,
    n_bins          = 4,
    quantile_bins   = TRUE
  )


explanation <- test_tbl %>%
  slice(1:20) %>%
  select(-Attrition) %>%
  lime::explain(
    explainer = explainer,
    n_labels   = 1,
    n_features = 8,
    n_permutations = 5000,
    kernel_width   = 0.5
  )

explanation <- explanation %>%  
  mutate(case = as.numeric(case)) %>%
  mutate(feature_desc = as.character(feature_desc)) %>%
  mutate(feature_desc2 = gsub("[^a-zA-Z]", "", feature_desc))%>% 
  mutate(feature_desc3 = gsub("[^0-9]", "", feature_desc))%>% 
  select(feature_desc,feature_desc2,feature_desc3,case, everything()) %>% 
  arrange(desc(feature_desc2)) %>% 
  group_by(feature_desc2,feature_desc3,case)%>%
  as.tibble()

ggplot(explanation, aes(x = case, y = fct_inorder(feature_desc), fill =feature_weight)) +
  facet_wrap(~ label) +
  geom_tile() + 
  scale_fill_gradientn(colours = c("#A42A2C", "white", "#2A6AA4"))+
  scale_x_continuous(breaks = seq(0, 20, 1), lim = c(0, 20)) +
  labs(
    title    = "",
    subtitle = "",
    x = "Case", 
    y = "Feature",
    fill = "Feature weight"
  )
```

# (Session 13 - Deep Learning) - OUT OF SCOPE
Out of Scope 

# Reporting
